Why Donors Donate

### 2023-11-20 README.qmd
Remove errant |>
User newer abstract

As space for civil society has closed around the world, transnational NGOs have faced a crisis of funding. We explore how NGOs have shifted from traditionally Northern funding sources toward grassroots private philanthropic money. How do individual donors in the US feel about donating to legally besieged NGOs abroad? Do legal restrictions on NGOs influence donors’ decision to donate? We use a conjoint survey experiment to argue that domestic political environments of NGO host countries influence preferences of private donors and that legal crackdowns on NGOs serve as a heuristic of organizational deservingness.

@@

codename(type = "nicka", seed = "why donors donate") |> 
#> [1] "silent skywalk"
```

>>>>

Non-governmental organizations (NGOs) are a core component of global governance. Over the last two decades, however, many host governments have cracked down on NGOs using a series of laws that adversely affect the availability and use of traditional NGO funding. In response to this dramatic shift in the funding landscape, international NGOs have increasingly turned to individual donors to offset the loss funding. Prior research on NGO fundraising has examined how financial transparency and organizational accountability influence individual donor behavior. How do these elements of private donor decision-making interact with structural-level factors such as worsening host country civic environments when deciding to donate? Using a conjoint experiment with likely donors in the US, we find that transparency and accountability can protect against the dampening effect of host government crackdown and criticism of NGOs. Our results have important implications for how NGOs can adapt to worsening civic environments.

@@

codename(type = "nicka", seed = "why donors donate")
#> [1] "silent skywalk"
```

### 2023-11-20 index.qmd
User newer abstract

Abstract goes here

>>>>

Non-governmental organizations (NGOs) are a core component of global governance. Over the last two decades, however, many host governments have cracked down on NGOs using a series of laws that adversely affect the availability and use of traditional NGO funding. In response to this dramatic shift in the funding landscape, international NGOs have increasingly turned to individual donors to offset the loss funding. Prior research on NGO fundraising has examined how financial transparency and organizational accountability influence individual donor behavior. How do these elements of private donor decision-making interact with structural-level factors such as worsening host country civic environments when deciding to donate? Using a conjoint experiment with likely donors in the US, we find that transparency and accountability can protect against the dampening effect of host government crackdown and criticism of NGOs. Our results have important implications for how NGOs can adapt to worsening civic environments.
